---
title: "Milo Rainleaf"
author: "skamkam"
date: "2023-06-09"
output: html_document
---

\setlength\parindent{25pt}
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE)
library(tidyverse)
library(knitr)
library(hash)
library(kableExtra)
```

# Character Sheet

```{r} 
# build the character sheet dataframe and display it
labels <- c("Stat", "Modifier")
STR <- c(10, "+0")
DEX <- c(11, "+0")
CON <- c(8, "-1")
INT <- c(15, "+2")
WIS <- c(13, "+2")
CHA <- c(18, "+4")

charsheet <- data.frame(labels, STR, DEX, CON, INT, WIS, CHA) %>% 
  rename(" " = labels)

kable(charsheet) %>% 
  kable_styling() %>% 
  column_spec(1, bold=T)

```

## Other Stats

**Hit points**: 42

- Number of hit dice: 6

**Inspiration**: [blank]

**Proficiency bonus**: +3

- Double proficiency bonus if performing a CHA check with dragons

**Perception check**: d20 + WIS modifier

**Initiative**: d20 + DEX modifier

**Saving throws**: CON, CHA

**Armor class**: 13 without armor (dragon scales)

- Dodge: DEX modifier + armor deflect

## Skills
- Religion [INT]
- Persuasion [CHA]
- Investigation [INT]
- Insight [WIS]

### Languages
Fluent in Common, Halfling, Draconic languages

### Weapon and tool proficiencies
- Daggers, darts, slings, quarterstaffs, light crossbows
- Navigator's tools, calligrapher's supplies

## Halfling Traits
- **Speed**: 25 feet base walking speed
- **Size**: ~ 3 feet tall, 40 lbs; size Small
- **Lucky**: When you roll a 1 on the d20 for an attack roll, ability check, or saving throw, you can reroll the die and must use the new roll
- **Brave**: Advantage on saving throws against being frightened
- **Halfling Nimbleness**: Can move through the space of any creature that is of a size larger than yours

# Spells

## Cantrips {.tabset}

### Acid Splash

```{r}
cast <- c("1 Action")
range <- c("60 ft")
Components <- c("V, S")
Duration <- c ("Instantaneous")
atk <- c("DEX save")
effect <- c("Acid")

acid_splash <- data.frame(cast, range, Components, Duration, atk, effect) %>% 
  rename("Casting Time" = cast, "Range/Area" = range, "Attack/Save" = atk, "Damage/Effect" = effect)

kable(acid_splash)
```

You hurl a bubble of acid. Choose one or two creatures you can see within range. If you choose two, they must be within 5 feet of each other. A target must succeed on a Dexterity saving throw or take 1d6 acid damage.

This spell’s damage increases by 1d6 when you reach 5th level (2d6), 11th level (3d6), and 17th level (4d6).


### Mending

### Light

### Control Flames

### Poison Spray

